### 2013-03-26 doc/sosp13/intro.tex
commit to merge

\noindent{\bf Low Injection Rate} Reference patterns of irregular
applications are unpredictable, with odds increasing as data is
spread out more broadly across a larger system that a given reference
will refer to memory located remotely.  This behavior constrasts
sharply with that of data-parallel applications for which efficient
frameworks such as MapReduce~\cite{mapreduce:osdi04} may exploit the
structure of computation and data affinity to limit internode
communication to less infrequent, larger messages.  Mass
market network technology is designed to transfer these larger blocks
of data, not the word-sized references emitted by irregular
application tasks. Injection rate into the network is insufficient to
utilize wire bandwidth when blocks are below about two-kilobytes, so
any naive communication strategy severely under-utilizes the network.

@@

\Grappa leverages as much freely available and commodity infrastructure as
possible. We use unmodified Linux for the operating system and an
off-the-shelf user-mode InfiniBand device driver stack~\cite{OFED}. MPI is
used for process setup and tear down. GASnet~\cite{gasnet} is used as the
underlying mechanism for remote memory reads and writes using active message
invocations. To this commodity hardware and software mix \Grappa adds three
main software components: (1) a \emph{lightweight tasking\/} layer that
supports a context switch in as few as 38ns and distributed global load
balancing; (2) a \emph{distributed shared memory\/} layer that supports normal
access operations such as \emph{read\/} and \emph{write\/} as well as
synchronizing operations such as \emph{fetch-and-add\/}~\cite{fetchandadd};
and (3) a \emph{communication\/} layer that combines short messages to
achieve peak bandwidth on commodity networks. As we will show later, \Grappa
can tolerate latencies way beyond that of the network. Therefore, \Grappa can
afford to \emph{trade latency for throughput}. By {\em increasing\/} latency
in key components of the system we are able to: increase effective random
access memory bandwidth by delaying and aggregating messages; increase
synchronization rate by delegating atomic operations to gatekeeper cores, even
when referencing node-local global data; and improve load balance by
tolerating the delays incurred when work-stealing.

>>>>

\noindent{\bf Low Injection Rate} Reference patterns of irregular
applications are unpredictable, with odds increasing as data is
spread out more broadly across a larger system that a given reference
will refer to memory located remotely.  This behavior contrasts
sharply with that of data-parallel applications for which efficient
frameworks such as MapReduce~\cite{mapreduce:osdi04} may exploit the
structure of computation and data affinity to limit internode
communication to less infrequent, larger messages.  Mass
market network technology is designed to transfer these larger blocks
of data, not the word-sized references emitted by irregular
application tasks. Injection rate into the network is insufficient to
utilize wire bandwidth when blocks are below about two-kilobytes, so
any naive communication strategy severely under-utilizes the network.

@@

\Grappa leverages as much freely available and commodity infrastructure as
possible. We use unmodified Linux for the operating system and an
off-the-shelf user-mode InfiniBand device driver stack~\cite{OFED}. MPI is
used for process setup and tear down. GASNet~\cite{gasnet} is used as the
underlying mechanism for remote memory reads and writes using active message
invocations. To this commodity hardware and software mix \Grappa adds three
main software components: (1) a \emph{lightweight tasking\/} layer that
supports a context switch in as few as 38ns and distributed global load
balancing; (2) a \emph{distributed shared memory\/} layer that supports normal
access operations such as \emph{read\/} and \emph{write\/} as well as
synchronizing operations such as \emph{fetch-and-add\/}~\cite{fetchandadd};
and (3) a \emph{communication\/} layer that combines short messages to
achieve peak bandwidth on commodity networks. As we will show later, \Grappa
can tolerate latencies way beyond that of the network. Therefore, \Grappa can
afford to \emph{trade latency for throughput}. By {\em increasing\/} latency
in key components of the system we are able to: increase effective random
access memory bandwidth by delaying and aggregating messages; increase
synchronization rate by delegating atomic operations to gatekeeper cores, even
when referencing node-local global data; and improve load balance by
tolerating the delays incurred when work-stealing.
